---
output: html_document
editor_options: 
  chunk_output_type: console
---


Now we are going to work with BAMM

```{r}
library(BAMMtools)
library(coda)

## load data
mytree <- read.tree("tree.tree")
mcmcout <- read.csv("mcmc_out.txt")

## create edata
edata <- getEventData(mytree, eventdata = "event_data.txt", burnin=0.15)


#### Check convergence
plot(mcmcout$logLik ~ mcmcout$generation)

burnstart <- floor(0.15 * nrow(mcmcout))
postburn <- mcmcout[burnstart:nrow(mcmcout), ]

effectiveSize(postburn$N_shifts)
effectiveSize(postburn$logLik)



### Shift probabilities
shift_probs <- summary(edata)
shift_probs


### Bayes factors
bfmat <- computeBayesFactors(postburn, expectedNumberOfShifts=1, burnin=0.15)
bfmat

#### PLOT CREDIBLE SHIFTS
css <- credibleShiftSet(edata, expectedNumberOfShifts=1, threshold=5, set.limit = 0.95)
css
plot.credibleshiftset(css,spex = "netdiv")


### PLOT BEST SHIFT
par(mfrow=c(1,1))
best <- getBestShiftConfiguration(edata, expectedNumberOfShifts=1)
best
plot.bammdata(best, lwd = 2,spex = "netdiv",label=T,cex=0.5)
axisPhylo()
addBAMMshifts(best, cex=3)
best$eventData

### RATE through time
st <- max(branching.times(mytree))
plotRateThroughTime(edata, intervalCol="red", avgCol="red", start.time=st, ylim=c(0,1), cex.axis=1,ratetype='netdiv')
text(x=30, y= 0.8, label="All Centaurium", font=4, cex=1.0, pos=4)

#OHER OPTIONS
sc <- distinctShiftConfigurations(edata, expectedNumberOfShifts = 1, threshold = 5)

phylorates <- plot(edata, breaksmethod='jenks', show = FALSE)
pdffn = paste0("bamm", ".histogram.pdf")
pdf(file=pdffn, width=6, height=6)
ratesHistogram(phylorates, plotBrks = FALSE, xlab = 'diversification rates')
dev.off()







```

Pagel Models

```{r}
library(phytools)
mydata <- read.csv("data.csv")
names(mydata)

Polyploidy <- mydata[,5]
names(Polyploidy) <- mydata[,1]
AncestralArea <- mydata[,3]
names(AncestralArea) <- mydata[,1]

Dispersal <- mydata[,4]
names(Dispersal) <- mydata[,1]

tree <- mytree


x <-  Polyploidy
x[x==0] <- "D"
x[x==1] <- "P"
y <- AncestralArea
y[y==0] <- "A"
y[y==1] <- "N"
fit.xy<-fitPagel3(tree,x,y,dep.var="xyc")
fit.x<-fitPagel3(tree,x,y,dep.var="xc")
fit.y<-fitPagel3(tree,x,y,dep.var="yc")

fit.xy
fit.x
fit.y

fit.xy.Polyploidy.AncestralArea <-fit.xy
fit.x.Polyploidy.AncestralArea <-fit.x
fit.y.Polyploidy.AncestralArea <-fit.y

pdffn = paste0("fit.x.Polyploidy.AncestralArea.pdf")
pdf(file=pdffn, width=8, height=8)
plot(fit.y.Polyploidy.AncestralArea,lwd.by.rate=TRUE,
    main=c("a) Independent model",
    "b) Dependent (Polyploidy | AncestralArea) model"))
dev.off()



y <- Dispersal
y[y==0] <- "N"
y[y==1] <- "W"
fit.xy<-fitPagel3(tree,x,y,dep.var="xyc")
fit.x<-fitPagel3(tree,x,y,dep.var="xc")
fit.y<-fitPagel3(tree,x,y,dep.var="yc")

fit.xy
fit.x
fit.y

fit.xy.Polyploidy.AncestralArea <-fit.xy
fit.x.Polyploidy.AncestralArea <-fit.x
fit.y.Polyploidy.AncestralArea <-fit.y

``

